### 2019-11-25 report/02-methods.Rmd
Test stab div relationship by spliting dataset in two

@@

>>>>

### Relationship between environmental variables

@@

#### Distribution of environmental variables

```{r dist-env, fig.cap = "Histogram of the station average environmental values through time."}

habitat_pressure %>%
  select(station, width_river_mean:temperature) %>%
  gather(env_var, value, width_river_mean:temperature) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(facets = ~ env_var, ncol = 3, scales = "free")
```

The figure \@ref[fig:dist-env] shows that, taking the environmental values one
by one, there was no apparent bimodality for habitat description such as
altitude, slope, distance from source, strahler order, river width and depth, flow, temperature.
However, variables such as latitude, insecticides, fungicides, herbicides
displayed bimodality. Those bimodalities will be helpful to test relationship
between stability and diversity for different subset of the dataset and so, test
the robustness of the relationship.

### 2019-11-25 report/05-stability.Rmd
Test stab div relationship by spliting dataset in two

```{r temp-grp}
myload(habitat_pressure, dir = mypath("report"))

>>>>

```{r}
myload(habitat_pressure, dir = mypath("report"))
```

```{r bimod-stab-div, fig.cap = "Relationship between stability and diversity by spliting dataset in two according to an environmental variable. The threshold for the dataset split is the median of the environmental variable."}
plot_bin_stab_div <- function (env = NULL) {

  habitat_pressure$env_bin <- ifelse(
    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
    "inf", "sup")
  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
  habitat_pressure %>%
    left_join(stab_div_basin, by = "station") %>%
    ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
    geom_point() +
    facet_grid(cols = vars(env_bin)) +
    stat_poly_eq(
      formula = y ~ x,
      eq.with.lhs = "italic(hat(y))~`=`~",
      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
      parse = TRUE) +
    geom_smooth(method = "lm", formula = y ~ x) +
    ggplot2::scale_color_manual(
      labels = troph_group_labeller(),
      values = c("blue", "green", "red"),
      name = "Trophic level"
    ) +
  labs(title = env, x = "Average species richness", y = "Biomass stability")
}

#width_river_mean avg_depth_station_mean
env <- c("width_river_mean", "avg_depth_station_mean", "lat", "long",
  "temperature", "flow", "d_source", "DBO")
mult_plot_stab_div_bin <- map(env, ~plot_bin_stab_div(env = .x))
plot_bin_stab_div(env = "width_river_mean")

plot_grid(plotlist = mult_plot_stab_div_bin)
